\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{comment} 
\newtheorem{problem}{Problem}

\newif\ifshowsolutions
\showsolutionsfalse

\ifshowsolutions
  \newenvironment{solution}{\par\noindent\textbf{Solution:}\itshape}{\par}
\else
  \excludecomment{solution}
\fi
  
\begin{document}
\begin{flushleft}
In high school, I never imagined majoring in mathematics. I saw myself as more inclined toward social sciences. However, my perspective shifted dramatically during college. I still vividly recall a moment when I submitted a completely incorrect solution to a problem set but received a surprisingly high grade because my professor found my approach intriguingly novel.\\
\bigskip
That experience sparked a deep interest in mathematics. I grew to love the process of grappling with challenging problems, often staying late at Lunt Hall or the McCormick Building. I would slip into empty classrooms, scribble problems on the blackboard, and immerse myself in finding solutions without consulting a manual.\\
\bigskip
This passion eventually led me to a career as a math instructor and problem-solving coach at ReachPrep in South Korea. To this day, I continue solving high school competition math problems. Some are still formidable, while others are less so. My primary interest lies in teaching the foundational concepts of competition math to younger students, helping them develop strong problem-solving skills.\\
\bigskip
In October 2024, I came across Dark Horse by Todd Rose, which deeply resonated with me. This project is inspired by Dark Horse and serves as a personal archive to track my progress as I pursue what I love. The problems featured here range from early AIME-level difficulty to the final seven questions of the AMC 10 or 12.\\
\newpage


\section*{November Archive}

\input{problems/November 2024.tex}


\end{flushleft}
\end{document}
