\begin{problem}
Bob can correctly answer each math problem on a mock test in $4$ minutes, and Bo can answer each problem per $1$ minute. Bo was so bored during the test, he took a nap for an hour in the middle of the test. Assuming that they started at the same time, they finished at the same time. How many questions were on the mock exam?
\end{problem}

\begin{solution}
Let $n$ be the number of problems in the mock test. Then, $n+60=4n$, so $3n=60$. The answer is $20$. 
\end{solution}

\begin{problem}
An energy drink is one-third caffeine and the rest water. If six ounces of water were added, it would make $20\%$ caffeine. How many ounces of total liquid (water plus caffeine) were in the original mixture?
\end{problem}

\begin{solution}
Notice that $3/15=1/5=20\%$. The answer is $9$. 
\end{solution}

\begin{problem}
A straight pole which was vertical is broken $36$ feet from the ground, and the top part comes down diagonally from the break until it touches the ground $27$ feet from the bottom of the pole. How many feet tall was the pole?
\end{problem}

\begin{solution}
Notice that $27:36:k=3:4:5$, so $k=45$. Hence, $45+36=81$ is the length of the pole. The answer is $81$.
\end{solution}

\begin{problem}
Bob runs around a circular track in the same amount of
time that Bo takes to run around a smaller concentric circular track. Bob is twice as fast as Bo, and is running on a track of circumference $120\pi$ meters. How many meters apart are the two tracks?
\end{problem}

\begin{solution}
The radius of the larger circle is $60$ meters. Since Bob is twice as fast as Bo, the radius of the smaller circle must be half of the larger one. The distance between the track must be $30$. Therefore, the answer is $30$. 
\end{solution}

\begin{problem}
Compute the product of the roots of the equation $|x|^2-5|x|+6=0$.
\end{problem}

\begin{solution}
Solving for $|x|$, we get $|x|=3,2$. Hence, $x=\pm3$ and $\pm2$. Thus, the product equals $36$. The answer is $36$.
\end{solution}

\begin{problem}
A die with the numbers $1$, $2$, $3$, $4$, $5$, and $6$ on its faces is biased in such a way that the probability that the number $j$ turns up is proportional to $j$. If the probability that an odd number turns up is $m/n$ where $m$ and $n$ are relatively prime, find $m+n$.
\end{problem}

\begin{solution}
Notice that $p(2, 4, 6)=\frac{2}{21}+\frac{4}{21}+\frac{6}{21}=\frac{12}{21}=\frac{4}{7}$. Hence, $m+n=4+7=11$. The answer is $11$.
\end{solution}

\begin{problem}
Given a circle centered at $O$, there exists an obtuse triangle $ABC$ inscribed in the circle such that $B$ is obtuse. If $AB=3$ and $BC=8$, and the height from $B$ to $\overline{AC}$ is $2$, the area of the circle can be written as $n\pi$. Find $n$.
\end{problem}

\begin{solution}
Let $h$ be the length of the height from $B$ to $\overline{AC}$. Then, by similarity, $AB:h=2R:BC$. Hence, $AB(BC)=h(2R)$. Thus, $24=4R$. The radius is $4$, so the area of the circle equals $16\pi$. The answer is $16$.
\end{solution}

\begin{problem}
Determine the remainder when $3^{15}+5^{15}$ is divided by $17$. 
\end{problem}

\begin{solution}
According to Fermat's Little Theorem, $3^{16}\equiv 5^{16} \equiv 1 \pmod{17}$.
\begin{align*}
    3^{15}+5^{15} & \equiv \frac13+\frac15 \pmod{17}\\
    & \equiv \frac{18}{3}+\frac{35}{5} \pmod{17}\\
    & \equiv 6+7 \pmod{17}\\
    & \equiv 13 \pmod{17}
\end{align*}
The answer is $13$.
\end{solution}

\begin{problem}
Given positive real numbers $a$, $b$, $c$, and $d$, if $(a+c)(b+d)=121$, determine the least value of $a+b+c+d$.
\end{problem}

\begin{solution}
According to AM-GM inequality, 
\begin{align*}
    \dfrac{(a+c)+(b+d)}{2} & \geq \sqrt{(a+c)(b+d)}\\
    \dfrac{a+b+c+d}{2} & \geq \sqrt{121}\\
    a+b+c+d &\geq 2(11)\\
    &\geq 22
\end{align*}
The answer is $22$.
\end{solution}

\begin{problem}
Given three positive integers $a>b>c\geq1$, let $N$ be the number of triples $(a,b,c)$ such that $a+b+c=331$. Find the last three digits of $N$.
\end{problem}

\begin{solution}
Stars-and-bars imply that the total number of triples without condition equals $\binom{333}{2}$. Assume that $a=b>c$. Then, $2a+c=331$. Diophantine equation shows $166$ triples. Arrange $166$ triples by $\frac{3!}{2!}=3$ ways. Hence, subtract $498$ from $55278$ to retrieve $54780$. The answer is $780$.
\end{solution}

\begin{problem}
Compute the number of sequences that are arrangements of the numbers $1$, $2$, $3$, $4$, and $5$ and satisfy the requirement that no term in the sequence is larger than or equal to the square of the next term.
\end{problem}

\begin{solution}
First, $1$ should stay in the front of the sequence. Notice that $1<2^2$, $3<2^2$ and $4=2^2$. Hence, we only allow $12$ or $32$ as two consecutive terms in the sequence. Arrange $3$, $4$, and $5$, in $3!(=6)$ ways. Then, place $2$ next to either $1$ or $3$, in $2!(=2)$ ways. Therefore, there are $12$ sequences satisfying the given condition. The answer is $12$.
\end{solution}

\begin{problem}
Determine the number of ordered pairs of positive integers $(a,b)$ such that $a^b=3^{3^3}$.
\end{problem}

\begin{solution}
Since $3^{3^3}$ is $3^{27}$. there is one-to-one correspondence between the number of divisors of $27$ and $(a,b)$. Hence, there are $4$ pairs of $(a,b)$. The answer is $4$.
\end{solution}

\begin{problem}
Compute the least positive integer value of $n$ such that $10n$ and $12n$ have the same number of divisors.
\end{problem}

\begin{solution}
Let $n=2^a3^b5^c$. $10n$ and $12n$ have the equal number of divisors if and only if $(a+2)(b+1)(c+2)=(a+3)(b+2)(c+1)$. The smallest value of $n$ can be retrieved when $a=0$, $b=2$ and $c=0$. Thus, the answer is $9$.
\end{solution}

\begin{problem}
On the complex plane there are six complex numbers satisfying $z^6=1$. Given that $z$, $z^2$ and $z^3$ form a non-degenerate triangle, the ratio between the smallest area and largest area formed by $z$, $z^2$ and $z^3$ can be written as $\frac{a}{b}$ where $a$ and $b$ are relatively prime integers. Find $a+b$.
\end{problem}

\begin{solution}
The smallest area is $\frac{\sqrt{3}}{4}$, whereas the largest area is $\frac{3\sqrt{3}}{4}$. Hence, the ratio equals $\frac{1}{3}$. The answer is $4$.
\end{solution}

\begin{problem}
Three customers in a grocery store saw there are five apples and four oranges. After they left, there was no lemon nor orange left. In how many ways would the customers buy these fruits such that each takes at least one fruit of ANY type?
\end{problem}

\begin{solution}
There are $315$ number of ways to distribute fruits to these customers. Apply De Morgan's Law and Principle of Inclusion and Exclusion. There are $87$ bad ways such that there is at least one person not buying any fruit. Hence, the answer is $228$.
\end{solution}

\begin{problem}
Determine the sum of $x$-intercepts of a graph of $f(x)=(x-2)^7-x^7-4$.
\end{problem}

\begin{solution}
The graphs of two functions $y=(x-2)^7$ and $y=x^7+4$ intersect at two real points. Let $x=r$. then, $x=2-r$ is also the real solution. Hence, the sum of two real $x$-intercepts equals $2$. The answer is $2$.
\end{solution}

\begin{problem}
Suppose $f(x)=x^3-x+1$ has roots $r$, $s$, and $t$. Determine $\frac{r^3}{r-1}+\frac{s^3}{s-1}+\frac{t^3}{t-1}$.
\end{problem}

\begin{solution}
According to Viete's formula, $f(r)=f(s)=f(t)=0$. Hence, $r^3=r-1$, $t^3=t-1$ and $s^3=s-1$. The answer is $3$. 
\end{solution}

\begin{problem}
Determine the maximum possible value of $xy$ if $x^2+5xy+y^2=1001$ for real $x$ and $y$.
\end{problem}

\begin{solution}
According to AM-GM inequality, $x^2+5xy+y^2\geq 7xy$. Hence, $xy\leq 143$. Check that $x=y=\sqrt{143}$. The answer is $143$.
\end{solution}

\begin{problem}
The sum $\sum_{k=2}^{100}\frac{1}{\binom{k}{2}}$ can be written as $\frac{m}{n}$ where $m$ and $n$ are relatively prime positive integers. Find $m+n$.
\end{problem}

\begin{solution}
This telescopes so the sum changes into $2(1-\frac{1}{101})=\frac{200}{101}$. The answer is $301$.
\end{solution}

\begin{problem}
There are three rows with three seats each. If Mary, May and Mo wish to sit down, in how many ways can they be seated in different rows and different columns?
\end{problem}

\begin{solution}
Send Mary, May, and Mo, in that order. Send Mary in $9$ different places. Then, May can only be sent to $4$ different places. Likewise, Mo can only be sent to $1$ place. The answer is $36$.
\end{solution}

\begin{problem}
In how many ways can four $($'s and $)$'s be arranged in a line such that $)$ must be written after $($?
\end{problem}

\begin{solution}
This is a typical Catalan number problem for $4\times4$. Hence, there are $\frac{1}{5}\binom{8}{4}=14$. The answer is $14$.
\end{solution}

\begin{problem}
Points $P$ and $Q$ lie outside and inside square $AIME$, respectively such that $\triangle API \cong \triangle MQI$ and $m\angle API = 90^\circ$. Suppose that $AP=1$ and $PQ=24$. Compute $[AIME]$ where $[AIME]$ refers to the area of $\square AIME$.
\end{problem}

\begin{solution}
Apply Pythagorean Theorem to conclude that $PI=12\sqrt{2}$ and $AP=1$, so $AI=17$. Hence, $AI^2=289=[AIME]$. The answer is $289$.
\end{solution}

\begin{problem}
A polynomial equation $x^3+px^2+12x+q=0$ has integer roots, one of which is $1$. Find the maximal possible value of $p$.
\end{problem}

\begin{solution}
According to Viete's formula, let $x^3+px^2+12x+q=(x-1)(x-a)(x-b)$ for two other solutions $a$ and $b$. Then, $(a+1)(b+1)=13$ implies that $(a,b)=(12,0)$, $(0,12)$, $(-14,-2)$ and $(-2,-14)$. Hence, $p=-a-b-1$ is either $15$ or $-13$. The largest possible value is $15$. The answer is $15$.
\end{solution}

\begin{problem}
Let $n$ be the number of degree $5$ polynomials $f(x)$ with non-negative integer coefficients such that $f(1)=10$ and $f(-1)=4$. Find the total possible number of $f(x)$s.
\end{problem}

\begin{solution}
Apply stars and bars twice to get $216(=36\times6)$ polynomials of $x$. The answer is $216$.
\end{solution}

\begin{problem}
Eunchan and Joochan made unit cubes, respectively, using magnetic balls and sticks. They decided to use all to make a new right prism, using all of the sticks and balls. They found out each of the faces is regular polygon. The volume of the new prism can be written as $a+\sqrt{b}$. Find $a+b$.
\end{problem}

\begin{solution}
This new solid is an octagonal prism. The base area equals $2+2\sqrt{2}$, and the height equals $1$. Hence, the volume equals $2+\sqrt{8}$. The answer is $10$.
\end{solution}

\begin{problem}
Three standard, fair six-sided die are rolled at a time. Given that the sum of the values rolled is $12$, the probability that at least two of the shown values is prime can be written as $\frac{m}{n}$ for relatively prime $m$ and $n$. Find $m+n$.
\end{problem}


\begin{solution}
\begin{align*}
a+b+c&=12\\
6+5+1&=12\\ 
6+4+2&=12\\
6+3+3&=12\\ 
5+5+2&=12\\ 
5+4+3&=12\\ 
4+4+4&=12
\end{align*}
Out of $216$ triples, there are $12$ triples satisfying this property. Hence, $\frac{12}{216}=\frac{2}{36}=\frac{1}{18}$. Hence, the answer is $19$.
\end{solution}

\begin{problem}
Determine the remainder when $111,111,111,111$ is divided by $17$.
\end{problem}

\begin{solution}
The answer is $7$.
\end{solution}

\begin{problem}
If four fair six-sided die are rolled, the probability that the average of four outcomes is $3$ can be written as $\frac{m}{n}$ where $m$ and $n$ are relatively prime positive integers. Determine $m+n$.
\end{problem}

\begin{solution}
The answer is $1421$.
\end{solution}

\begin{problem}
Given a right isosceles triangle $ABC$ where $AB=BC=3$ and $AC=3\sqrt{2}$, the probability that a point inside the triangle is closer to $AC$ than to either $AB$ or $BC$ can be written as $\sqrt{a}-b$ where $a$ and $b$ are positive integers, and $a$ is a square-free integer. Determine $a+b$.
\end{problem}

\begin{solution}
The answer is $3$.
\end{solution}

\begin{problem}
Suppose $\overline{AB}$ and $\overline{BC}$ are the chords of the same circle centered at $O$ such that their perpendicular bisectors meet at $O$. If $AB=4$ and $BC=7$, then the area of circle can be written as $\frac{a\pi}{b}$ where $a$ and $b$ are relatively prime positive integers. Determine the value of $ab$.
\end{problem}

\begin{solution}
The answer is $260$.
\end{solution}

\begin{problem}
If four fair six-sided die are rolled, the probability that the four outcomes, possibly rearranged if necessary, form an arithmetic sequence allowing the common difference of $0$, can be written as a reduced fraction $\frac{m}{n}$ where $m$ and $n$ are relatively prime positive integers. Determine the value of $m$.
\end{problem}

\begin{solution}
The answer is $13$.
\end{solution}

\begin{problem}
Two circles of different radii are tangent at a point $P$. If an external tangent to two circles meets the internal tangent line passing through $P$ at a point $Q$. Find $PQ^2$ if two radii are $7$ and $3$, respectively.
\end{problem}

\begin{solution}
The answer is $21$.
\end{solution}

\begin{problem}
Determine the sum of the digits of $111,111,111^2$.
\end{problem}

\begin{solution}
The answer is $81$.
\end{solution}

\begin{problem}
Given a right triangle with side lengths $6$, $8$, and $10$, if $H$ is the orthocenter, $O$ is the circumcenter, let $P$ be the midpoint of $\overline{OH}$. If $G$ is the centroid of the triangle, then the length of $PG$ can be written as $\frac{m}{n}$ where $m$ and $n$ are relatively prime positive integers. Determine $m+n$.
\end{problem}

\begin{solution}
The answer is $11$.
\end{solution}

\begin{problem}
Given a quadrilateral $ABCD$ where $AB=8$, $BC=6$, $CD=5\sqrt{2}$ and $AD=5\sqrt{2}$, if $\angle B$ and $\angle D$ are right angles, then $BD$ can be written as $a\sqrt{b}$ where $a$ and $b$ are positive integers, and $b$ is a square-free. Determine $a+b$.
\end{problem}

\begin{solution}
The answer is $9$.
\end{solution}

\begin{problem}
For a $4$-digit positive integer $n$, if $n^2$ and $n$ has the same remainder when divided by $100$, find the number of all such $n$ satisfying the given condition.
\end{problem}

\begin{solution}
The answer is $360$.
\end{solution}

\begin{problem}
Determine the smallest positive integer $n$ such that $n!$ end with exactly $10$ zeros.
\end{problem}

\begin{solution}
The answer is $45$.
\end{solution}

\begin{problem}
If $20a+23b=2023$ for non-negative integers $a$ and $b$, determine the total number of $(a,b)$ pairs satisfying the given equation.
\end{problem}

\begin{solution}
The answer is $5$. Here is one way of solving the problem.\\
	Let $a$ and $b$ be non-negative integers satisfying $20a+23b=2023$. Then,
	\begin{align*}
		20a+23b&=2023\\
		0a+3b&\equiv 3 \pmod{20}\\
		3b&\equiv 3 \pmod{20}\\
		b&\equiv 1 \pmod{20}
	\end{align*}
	Hence, $b=20k+1$ for some integer $k$. Since $23b=2023-20a\leq 2023$, we set $b\leq 87\frac{22}{23}$. Hence, $20k+1 \leq 87\frac{22}{23}$ implies that $0\leq k \leq 4$. Thus, there are $5$ values of $k$.
\end{solution}

\begin{problem}
Given a monic cubic polynomial equation $x^3-5x^2+7x-11=0$ with solutions $r$, $s$, and $t$, determine the exact value of $r^3+s^3+t^3$.
\end{problem}

\begin{solution}
The answer is $53$. Here is one way of solving the problem. Let $r$, $s$, and $t$ be the solutions to the given polynomial equation. Then, by Viete's formula,
	\begin{align*}
		x^3-5x^2+7x-11 &= (x-r)(x-s)(x-t)\\
		x^3-5x^2+7x-11 &= x^3-(r+s+t)x^2+(rs+st+tr)x-rst
	\end{align*}
	Thus, we conclude that $r+s+t=5$, $rs+st+tr=7$ and $rst=11$.\\
	\bigskip
	According to algebraic identity of cubic sums, we get
	\begin{align*}
	r^3+s^3+t^3-3rst &= (r+s+t)(r^2+s^2+t^2-rs-st-tr)\\
	r^3+s^3+t^3 &= (r+s+t)(r^2+s^2+t^2-rs-st-tr)+3rst\\
	&= (r+s+t)((r+s+t)^2-3(rs+st+tr))+3rst\\
	&=5((5^2)-3(7))+3(11)\\
	&=20+33\\
	&=53
	\end{align*}
	Another way to solve this problem is to use Newton's Identity. Let $S_1=r+s+t$, $S_2= r^2+s^2+t^2$, and $S_3=r^3+s^3+t^3$. Then, by Newton's identity,
	\begin{align*}
		S_1-5(1)&=0\\
		S_2-5S_1+7(2)&=0\\
		S_3-5S_2+7S_1-11(3)&=0
	\end{align*}
	Hence, $S_1=5$, $S_2=11$, and $S_3=53$.
\end{solution}

\begin{problem}
For a quadratic function $f(x)=x^2-2$, for real $(x,y)$, if $|x|+2|y|\leq2$, then the minimum possible value of $f(x)$ can be written as $\frac{-a+\sqrt{b}}{c}$ where $a$, $b$, and $c$ are positive integers, and $b$ is a square-free integer. Determine the sum $a+b+c$. (Terminology: a square-free integer is a positive integer that is not divisible by any perfect square (other than 1).)
\end{problem}

\begin{solution}
The answer is $32$.\\
	\begin{center}
	\begin{tikzpicture}
		% Set the limits of the x and y axes
		\def\xmin{-3}
		\def\xmax{3}
		\def\ymin{-3}
		\def\ymax{3}
		
		\clip (\xmin,\ymin) rectangle (\xmax+1,\ymax+1);
		
		\draw  (-2,0)--(0,1)--(2,0)--(0,-1)--cycle;
		\filldraw[gray!20] (-2,0)--(0,1)--(2,0)--(0,-1)--cycle;
		
		% Draw the graph of y = x^2 - 2
		\draw[domain=\xmin:\xmax, smooth, samples=100] plot (\x,{\x*\x - 2});
		\draw[latex-latex] (\xmin,0) -- (\xmax,0) node[right] {$x$};
		\draw[latex-latex] (0,\ymin) -- (0,\ymax) node[above] {$y$};
	\end{tikzpicture}
	\end{center}
As one can see from the figure above, $x^2-2=\frac{1}{2}x-1$ or $x^2-2=-\frac{1}{2}x-1$ result in the minimum possible value of $f(x)$. Hence, solving the equations, we get either $2x^2-4=x-2$ or $2x^2-4=-x-2$. Since $2x^2-x-2=0$ or $2x^2+x-2=0$, we get $x=\frac{1-\sqrt{15}}{4}$ or $\frac{-1+\sqrt{15}}{4}$.\\
\bigskip
The first solution will result in 
\begin{align*}
	y=-\frac{1}{2}x-1=-\frac{1}{2}\left(\frac{1-\sqrt{15}}{4}\right)-1=\frac{-9+\sqrt{15}}{8}
\end{align*}
Similarly, the second solution will result in 
\begin{align*}
	y=\frac{1}{2}x-1=\frac{1}{2}\left( \frac{-1+\sqrt{15}}{4} \right) -1 = \frac{-9+\sqrt{15}}{8}
\end{align*}
Hence, $a=9$, $b=15$, and $c=8$. Thus, $a+b+c=9+15+8=32$.\\
\end{solution}

\begin{problem}
Given an equilateral triangle $ABC$ of side length $6$, suppose there is a square $PQRS$ inside the triangle such that three of its vertices are on the sides of the square, i.e., $\overline{AB}$, $\overline{BC}$, $\overline{AC}$. If $P$ is on the midpoint of $\overline{BC}$, $Q$ and $S$ are on $\overline{AB}$ and $\overline{AC}$, respectively, then $QS=a-b\sqrt{c}$ if $A$, $R$, and $P$ are collinear. If $a$, $b$, and $c$ are positive integers such that $c$ is a square-free integer, determine the product $abc$.\\
\end{problem}

\begin{solution}
The answer is $81$. It is clear that $m\angle QPB = m \angle SPC = 45^\circ$, since $A$, $R$, and $P$ are collinear. Let $O$ be the intersection point between $\overline{QS}$ and $\overline{AP}$. Then, we may label $QO=RO=SO=OP=k$. This implies that 
\begin{align*}
	BQ&=\frac{2k}{\sqrt{3}}=\frac{2\sqrt{3}k}{3}\\
	AQ&=6-\frac{2\sqrt{3}k}{3}
\end{align*}
Since $AQS$ is an equilateral triangle, we may use $\frac{AQ}{OQ}=\frac{1}{2}$. Hence, $\frac{6-\frac{2\sqrt{3}k}{3}}{k}=\frac{1}{2}$. Thus, $k=\frac{9-3\sqrt{3}}{2}$. Since $QS=PR=2k$, we conclude that $QS=a-b\sqrt{c}=9-3\sqrt{3}$. Thus, $a=9$, $b=3$, and $c=3$. Therefore, $abc=9\cdot3\cdot3=81$.\\
\bigskip
Similarly, if we use the laws of sines, 
\begin{align*}
	\frac{QP}{BP}&=\frac{k\sqrt{2}}{3}\\
	&=\frac{\sin(60^\circ)}{\sin(75^\circ)}\\
	&=\frac{\sqrt{3}/2}{(\sqrt{6}+\sqrt{2})/4}\\
	&=\frac{2\sqrt{3}}{\sqrt{6}+\sqrt{2}}
\end{align*}
Hence, $k=\frac{36-12\sqrt{3}}{8}$. Thus, $2k=QS=9-3\sqrt{3}$. Hence, $abc=81$.
\end{solution}

\begin{problem}
Given a piece-wise function $f(x)$ defined on $0\leq x \leq 2$ and $0\leq y \leq 2$ such that
$$\begin{cases} x+1 & (0\leq x < 1) \\ 4-2x & (1\leq x \leq 2) \end{cases},$$ the graph of $y=f(f(f(x)))$, the $x$-axis and the vertical line $x=2$ form a bounded region. The area of the bounded region can be written as $\frac{m}{n}$ where $m$ and $n$ are relatively prime positive integers. Determine $m+n$.
\end{problem}

\begin{solution}
The answer is $27$. Students learn sketching the graph of composition of functions in the first semester of Precalculus or second semester of Algebra 2. The graph of $y=f(f(f(x)))$ is given by the following figure.
\begin{center}
	\begin{tikzpicture}[scale=1.5]
		\draw[-latex] (-0.5,0)--(3,0);
		\draw[-latex] (0,-0.5)--(0,3);
		\draw[dotted] (2,0)--(2,2)--(0,2);
		\draw (0,0)--(0.5,2)--(1,1)--(1.25,2)--(1.5,0)--(2,2);
		\draw (0.5,2)--(0.5,0) [dotted];
		\draw (0,1)--(1,1)--(1,0) [dotted];
		\draw (1.25,2)--(1.25,0) [dotted];
		\node[below] at (0.5,0) {$\frac12$};
		\node[below] at (1,0) {$1$};
		\node[below] at (1.25,0) {$\frac54$};
		\node[below] at (1.5,0) {$\frac32$};
		\node[below] at (2,0) {$2$};
		\node[left] at (0,2) {$2$};
		\node[left] at (0,1) {$1$};
		\node[right] at (3,0) {$x$};
		\node[above] at (0,3) {$y$};
	\end{tikzpicture}
\end{center} 
Hence, the area bounded by the graph of $y=f(f(f(x)))$, the $x$-axis, and the vertical line $x=2$ can be computed as 
\[
\frac12+\frac34+\frac38+\frac14+\frac12=2+\frac38=\frac{19}{8}
\]
Thus, $m=19$ and $n=8$. The sum of $m$ and $n$ is $27$.\\
\end{solution}

\begin{problem}
Given a set of integers $\{1,2,3,4,5,6,7,8,9\}$, if five integers, not necessarily distinct, are chosen at random, as $a$, $b$, $c$, $d$, and $e$, respectively, the probability that $a\leq b < c \leq d \leq e$ can be written as $\frac{m}{n}$ where $m$ and $n$ are relatively prime positive integers. Determine the exact value of $m$. (In this problem, make sure that $b<c$.)
\end{problem}

\begin{solution}
The answer is $88$. We perform caseworks.
\begin{enumerate}
	\item $a=b<c=d=e$ implies that there are $\binom{9}{2}$ choices for $(a,b,c,d,e)$.
	\item $a<b<c=d=e$ implies that there are $\binom{9}{3}$ choices for $(a,b,c,d,e)$.
	\item $a<b<c<d=e$ implies that there are $\binom{9}{4}$ choices for $(a,b,c,d,e)$.
	\item $a<b<c<d<e$ implies that there are $\binom{9}{5}$ choices for $(a,b,c,d,e)$.
	\item $a=b<c<d<e$ implies that there are $\binom{9}{4}$ choices for $(a,b,c,d,e)$.
	\item $a=b<c=d<e$ implies that there are $\binom{9}{3}$ choices for $(a,b,c,d,e)$.
	\item $a=b<c<d=e$ implies that there are $\binom{9}{3}$ choices for $(a,b,c,d,e)$.
	\item $a<b<c=d<e$ implies that there are $\binom{9}{4}$ choices for $(a,b,c,d,e)$.
\end{enumerate}
Hence, we use the hockey-stick identity to compute the following expression, i.e.,
\begin{align*}
	&\binom92+\binom93+\binom94+\binom95+\binom94+\binom93+\binom93+\binom94\\
	&= \binom{10}{3}+\binom{10}{5}+\binom{10}{4}+\binom{10}{4}\\
	&=\binom{11}{4}+\binom{11}{5}\\
	&=\binom{12}{5}
\end{align*}
Thus, the probability $\frac{m}{n}$ is equivalent to $\frac{11\cdot9\cdot8}{9\cdot9\cdot9\cdot9\cdot9}=\frac{88}{6561}$. Hence, $m=88$.
\end{solution}

\begin{problem}
Given a regular pentagon cut into five congruent triangles with their common vertices in the middle of the figure, Bob is coloring each triangle with three different pastes - blue, red or orange - allowing repetitions. Determine the number of distinct pentagon colorings such that blue triangles must not be adjacent to red ones, if any.
\end{problem}

\begin{solution}
The answer is $83$. We may use recursion and tree diagram. If the first region is colored with blue, then the second region can be colored either blue or orange. Likewise, if the first region is colored with red, then the second region can be colored either red or orange. On the other hand, if the first region is colored with orange, then the second region can be colored either blue, red, or orange.\\
\bigskip
If we begin coloring the first region by blue, then the fifth region can be colored with some pastes, according to the given condition can be counted as $29$, in total. However, since the fifth region cannot be colored as red, we must eliminate all red regions that occurred in the fifth region-coloring. Hence, there are $21$ possible ways to color the fifth region, still satisfying the given condition.\\
\bigskip
Likewise, if we begin coloring the first region by red, the symmetric counting implies that there are $21$ possible colorings of the fifth region.\\
\bigskip
On the other hand, if we begin coloring the first region by orange, then there are $41$ ways to color the fifth region, using the basic recursive form. Since there is no limitation on orange, we keep all $41$ colorings as valid counts. Hence, we take the sum of all possible colorings as $21+21+41=83$.\\ 
\end{solution}

\begin{problem}
Given a positive $9$-digit integer such that there are three $2$'s, three $4$'s and three $0$'s, determine the total number of positive $9$-digit integers divisible by $12$.
\end{problem}

\begin{solution}
The answer is $770$. The sum of all $9$ digits is already divisible by $3$ by default. Hence, we perform caseworks for divisibility by $4$.\\
\begin{enumerate}
	\item If the last two digits are $00$, then there are $\binom{7}{3,3}-\binom{6}{3,3}=120$ number of ways to arrange the remaining digits for $9$-digit integer.
	\item If the last two digits are $20$, then there are $\binom{7}{3,2,2}-\binom{6}{2,3}=150$ number of ways to arrange the remaining digits for $9$-digit integer.
	\item If the last two digits are $24$, then there are $\binom{7}{3,2,2}-\binom{6}{2,2,2}=120$ number of ways to arrange the remaining digits for $9$-digit integer.
	\item If the last two digits are $40$, then there are $\binom{7}{3,2,2}-\binom{6}{3,2}=150$ number of ways to arrange the remaining digits for $9$-digit integer.
	\item If the last two digits are $44$, then there are $\binom{7}{3,3}-\binom{6}{3,2}=80$ number of ways to arrange the remaining digits for $9$-digit integer.
	\item If the last two digits are $04$, then there are $\binom{7}{3,2,2}-\binom{6}{3,2}=150$ number of ways to arrange the remaining digits for $9$-digit integer.
\end{enumerate}
Hence, there are $770$ positive $9$-digit integers divisible by $12$.
\end{solution}

\begin{problem}
There is a closed region formed by connecting $(232023,232023)$, $(232019,232014)$, $(232022, 232022)$,  $(232014,232019)$, and back to $(232023,232023)$, in the written order. Determine the area of closed region.
\end{problem}

\begin{solution}
The answer is $5$. Since the area of the figure will not change under translation, we translate all the points by applying $$(x',y')=(x-232014,y-232014).$$ Have a look at the following figure. 
\begin{center}
	\begin{tikzpicture}[scale=0.7]
		\draw (0,0)--(9,0)--(9,9)--(0,9)--cycle [dotted];
		\draw (0,5)--(9,9)--(5,0)--(8,8)--cycle;
		\node[left] at (0,5) {$(0,5)$};
		\node[below left] at (0,0) {$(0,0)$};
		\node[below] at (5,0) {$(5,0)$};
		\node[above] at (9,9) {$(9,9)$};
		\node[right] at (10,8) {$(8,8)$}; 
		\draw[latex-] (8,8)--(10,8) [dotted];
		\filldraw (5,0) circle (2pt);
		\filldraw (0,5) circle (2pt);
		\filldraw (8,8) circle (2pt);
		\filldraw (9,9) circle (2pt);
	\end{tikzpicture}
\end{center}
The shoelace theorem suggests that 
\[
\text{Area}= \frac{1}{2}|(9\cdot5+0\cdot8+8\cdot0+5\cdot9)-(9\cdot0+5\cdot8+8\cdot5+0\cdot9)| = \frac{1}{2} |10| = 5
\]
\end{solution}

\begin{problem}
Given a square $ABCD$ of side length $4$, a special laser point is shot from $A$ to a point $P_1$ on $\overline{BC}$ such that $AB:BP_1=4:1$. This laser is so special that it reflects to a point $P_2$ on $\overline{CD}$ such that $AP_1P_2$ is a right angle. Then, a laser will be shot to a point $P_3$ on $\overline{AD}$ such that $P_1P_2P_3$ is right. This process continued until there are $P_1$ on $\overline{BC}$, $P_2$ on $\overline{CD}$, $P_3$ on $\overline{AD}$ and $P_4$ on $\overline{AP_1}$. The area of $P_1P_2P_3P_4$ can be written as $\frac{m}{n}$ where $m$ and $n$ are relatively prime positive integers. Determine $m+n$.
\end{problem}

\begin{solution}
The answer is $727$. Let's draw a figure, focusing on the similar triangles. 
\begin{center}
	\begin{tikzpicture}
		\draw (0,0)--(4,0)--(4,4)--(0,4)--cycle;
		\draw (0,4)--(1,0)--(4,3/4)--(51/16,4)--(3/16,13/4);
		\node[left] at (0,2) {$4$};
		\node[below] at (0.5,0) {$1$};
		\node[below] at (1,0) {$P_1$};
		\node[right] at (4,3/4) {$P_2$};
		\node[above] at (51/16,4) {$P_3$};
		\node[left] at (-0.5,13/4) {$P_4$};
		\draw[latex-latex] (-0.5,13/4)--(3/16,13/4);
		\filldraw (1,0) circle (2pt);
		\filldraw (4,3/4) circle (2pt);
		\filldraw (51/16,4) circle (2pt);
		\filldraw (3/16, 13/4) circle (2pt);
		\node[above] at (0,4) {$A$};
		\node[below] at (0,0) {$B$};
		\node[below] at (4,0) {$C$};
		\node[above] at (4,4) {$D$};
	\end{tikzpicture}
\end{center}
Since $CP_1:CP_2=4:1$, it is easy to find out $CP_2=\frac34$. Hence, $P_1P_2=\frac{3\sqrt{17}}{4}$. Since $P_2D=\frac{13}{4}$, the similar triangle ratio implies that $P_2P_3=\frac{13\sqrt{17}}{16}$. Thus, the area of $P_1P_2P_3P_4$ can be computed as the area of rectangle, i.e., 
\[
\frac{3\sqrt{17}}{4}\times\frac{13\sqrt{17}}{16}=\frac{39\cdot17}{64}=\frac{663}{64}
\]
Hence, $m+n=663+64=727$.
\end{solution}

\begin{problem}
Given a real valued function $f(x)=\{x\}=x-\lfloor x \rfloor$, where $\lfloor x \rfloor$ is the greatest integer less than or equal to $x$, and $g(x)=\sin(2\pi x)$, let $h(x)=f(g(x))$. Then, there exist $n$ number of solutions satisfying $h(h(x))=x$. Determine the exact value of $n$.
\end{problem}

\begin{solution}
The answer is $16$. In particular, at $0\leq x \leq \frac14$, the value of $h(x)$ shifts from $0$ to $1$, meaning that $h(h(x))$ must graph the full portion of $y=h(x)$ squeezed inside the interval $[0,\frac14]$. At $\frac14\leq x \leq \frac12$, the value of $h(x)$ shifts from $1$ to $0$, meaning that $h(h(x))$ must graph the full portion of $y=h(x)$ in reverse direction inside the given interval. We perform such graphing skill-sets in order to graph $y=h(h(x))$. Hence, we directly compute the number of intersections between $y=h(h(x))$ and $y=x$ as $16$ different points.
\end{solution}

\begin{problem}
Determine the exact value of \[\left(\cos(\frac{2\pi}{2023})+\cos(\frac{4\pi}{2023})+\cos(\frac{6\pi}{2023})+\cdots+\cos(\frac{4044\pi}{2023})\right)^2.\]
\end{problem}

\begin{solution}
The answer is $1$. Notice that $z^{2023}=1$ produces $2023$ roots of unity such that $z_{k}=\cos(\frac{2\pi k}{2023})+i\sin(\frac{2\pi k}{2023})$ for $k=0,1,2,\cdots,2022$ is a unique solution to the given equation. Now, have a look at $z^{2023}-1=0$. The sum of solutions must be $0$ by Viete's formula. In other words, 
$$
(\cos(0)+\cos(\frac{2\pi}{2023})+\cdots+\cos(\frac{4044\pi}{2023}))+i(\sin(0)+\sin(\frac{2\pi}{2023})+\cdots+\sin(\frac{4044\pi}{2023}))= 0+0i
$$
Hence, $\cos(\frac{2\pi}{2023})+\cos(\frac{4\pi}{2023})+\cdots+\cos(\frac{4044\pi}{2023})=-1$. Thus, $(-1)^2=1$.
\end{solution}

\begin{problem}
Let $ABCD$ be a parallelogram such that $m\angle B <90^\circ$ and $AB<BC$. Let $H$ be the intersection point between the altitude from $A$ to $\overline{BC}$ and the altitude from $C$ to $\overline{AB}$. Let $P$ and $Q$ be the perpendicular foot from $A$ to $\overline{BC}$ and from $C$ to $\overline{AB}$, respectively. If $QH:AH:PH=1:3:4$, then $\tan^2(\angle HDC)$ can be written as $\frac{m}{n}$ where $m$ and $n$ are relatively prime positive integers. Determine $m+n$.
\end{problem}

\begin{solution}
The answer is $177$. Let $AH=3k$, $QH=k$, and $PH=4k$. Then, by similar triangles formed by orthocenter, it is easy to find out that $CH=12k$ and $AB=\frac{21\sqrt{8}}{8}k$. Since $Q$ is the perpendicular foot from $C$ to $\overline{AB}$, it is clear that $\angle DCH$ is right. Hence, $\tan(\angle HDC)$ can be written as $\frac{CH}{CD}$. Since $CH=12k$ and $CD=AB=\frac{21\sqrt{8}}{8}k$, we conclude that
\begin{align*}
	\tan(\angle HDC)&=\dfrac{12k}{21\sqrt{8}k/8}\\
	&=\frac{96}{21\sqrt{8}}\\
	&=\frac{12\sqrt{8}}{21}\\
	&=\frac{4\sqrt{8}}{7}\\
	\tan^2(\angle HDC)&=\frac{16\cdot 8}{49}\\
	&=\frac{128}{49}
\end{align*}
Thus, $m=128$ and $n=49$. The sum of $m$ and $n$ can be computed as $177$.
\end{solution}

\begin{problem}
Given a regular hexagon labeled as $ABCDEF$, Bob the ant walks along its edge every minute, not changing its direction midway. He may walk the same path repeatedly, and he randomly selects the edges he may walk. For instance, if he stays at $B$, he may go to either $A$ or $C$ with equal likelihood. If Bob starts at one vertex, let's say $A$, determine the expected number of minutes it will take him to go visit the opposite vertex  $D$ for the first time.
\end{problem}

\begin{solution}
The answer is $9$. Let $E_X$ be the expected number of minutes it will take Bob to go visit the opposite vertex $D$ for the first time. Due to symmetry, let $E_Y$ be the expected number of minutes it will take Bob to go from either $B$ or $F$ to visit the vertex $D$ for the first time. Also, due to symmetry, let $E_Z$ be the expected number of minutes it will take Bob to go from either $C$ or $E$ to visit the vertex $D$ for the first time.\\
\bigskip
First, $E_X=\frac{1}{2}(1+E_Y)+\frac{1}{2}(1+E_Y)$, so $E_X=1+E_Y$.\\
Second, $E_Y=\frac{1}{2}(1+E_X)+\frac{1}{2}(1+E_Z)=1+\frac{1}{2}E_X+\frac{1}{2}E_Z$.\\
Third, $E_Z=\frac{1}{2}(1+E_Y)+\frac{1}{2}(1)$.\\
\bigskip
Hence, we get the system of equations of $E_X$ and $E_Y$ such that
\[
\begin{cases}
	E_X=1+E_Y\\
	E_Y=1+\frac12E_X+\frac12(1+\frac12E_Y)
\end{cases}
\]
Solving for $E_X$ and $E_Y$, we get $(E_X,E_Y)=(9,8)$. Hence, Bob will be expected to spend $9$ minutes before he reaches the opposite vertex $D$ for the first time.
\end{solution}

\begin{problem}
Assume that $m$ and $n$ are positive integers. Let $a_{m,m}=1$ for integers $m$. If $a_{m+1,n}=a_{m,n}+2m$ and $a_{m,n+1}=a_{m,n}-2n$ for integers $m$ and $n$, determine the number of distinct $(m,n)$ satisfying $a_{m,n}=2023$.
\end{problem}

\begin{solution}
The answer is $4$. First, let's fix $n=1$. Then,
\begin{align*}
	a_{2,1}&=a_{1,1}+2(1)\\
	a_{3,1}&=a_{2,1}+2(2)\\
	\vdots &= \vdots\\
	a_{m,1}&=a_{m-1,1}+2(m-1)
\end{align*}
Hence, $a_{m,1}=a_{1,1}+2(1+2+\cdots+m-1)=1+(m-1)m$. Now, we free the values of $n$.
\begin{align*}
	a_{m,2}&=a_{m,1}-2(1)\\
	a_{m,3}&=a_{m,2}-2(2)\\
	\vdots&=\vdots\\
	a_{m,n}&=a_{m,n-1}-2(n-1)
\end{align*}
Hence, $a_{m,n}=a_{m,1}-2(1+2+3+\cdots+n-1)=1+(m-1)m-(n-1)n=2023$.\\
This implies $m^2-m-n^2+n=2022$, so $(m-n)(m+n)-(m-n)=2022$. Therefore, $(m-n)(m+n-1)=2022$. Since the difference between $m-n$ and $m+n-1$ is $2n-1$, the parity must be different. Also, since $n\geq 1$, $2n-1\geq1$. This implies that $m-n<m+n-1$. Furthermore, $m+n-1>0$ implies that $m-n>0$. Thus, $(m-n,m+n-1)=(1,2022)$, $(2,1011)$, $(3,674)$ and $(6,337)$. Since there are $4$ different pairs for $(m-n,m+n-1)$, there must be $4$ different pairs for $(m,n)$, by one-to-one correspondence.
\end{solution}

\begin{problem}
Alice likes riding a sleigh in winter. As the lift is broken, she walks up to the top of a hill at the rate of $2$ kilometers per hour, and comes down the hill at $10$ kilometers per hour. Ignoring any time spent as she prepares to ride a sleigh on top of a hill, the average speed of the round trip, in kilometers per hour, can be written as $\frac{m}{n}$ where $m$ and $n$ are relatively prime integers. Compute $m+n$.
\end{problem}

\begin{solution}
The answer is $13$.
\end{solution}

\begin{problem}
Two concentric circles of radius $10$ and $12$ are drawn in a plane. A chord of the larger circle is tangent to the smaller circle. If the length of the chord can be written as $\sqrt{p}$ where $p$ is a composite number, compute $p$.
\end{problem}

\begin{solution}
The answer is $44$.
\end{solution}

\begin{problem}
If the square of the length of circumradius of a triangle with integer sides of length $11$, $12$, and $13$ can be written as $\frac{m}{n}$ where $m$ and $n$ are relatively prime integers, compute the value of $n$.
\end{problem}

\begin{solution}
The answer is $70$.
\end{solution}

\begin{problem}
A round-table with 12 equally-spaced seats is to be filled with people whose label-tags start from $1$ to $12$. If the sum of the label-tags on each person on every three consecutive seats is divisible by $3$, then the number of acceptable arrangements of all 12 people around the round table, assuming that two arrangements are considered \underline{distinct} even if one can be obtained from the other by rotating the table, can be computed as $N$. Find the sum of its digits.
\end{problem}

\begin{solution}
The answer is $16$.
\end{solution}

\begin{problem}
If $\overline{ABBC}$, a four-digit number divisible by $4$, satisfies the following condition $A\neq B \neq C$, compute the number of such $\overline{ABBC}$.
\end{problem}

\begin{solution}
The answer is $160$.
\end{solution}

\begin{problem}
If all positive integers are written in successive manner, i.e., \[123456789101112\cdots\] compute the digit that appears in $2022$nd position.
\end{problem}

\begin{solution}
The answer is $0$.
\end{solution}

\begin{problem}
If a circle is inscribed in a square whose sides are $10$, let there be a right isosceles triangle whose vertex is on top-right corner of a square such that its hypotenuse is tangent to the circle. If the side length of the right isosceles triangle can be written as $p-q\sqrt{r}$, where $p$, $q$, and $r$ are positive integers and $r$ is square-free, find $p+q+r$.
\end{problem}

\begin{solution}
The answer is $17$.
\end{solution}

\begin{problem}
If a quartic polynomial $x^4+\cdots+337x^2+\cdots+13$ can be factorized into $(x^2+ax+b)(x^2+cx+d)$ where $a$, $b$, $c$, and $d$ are non-composite positive integers, compute the sum of $a$ and $c$. (Here, non-composite integers consist of either $1$ or primes.)
\end{problem}

\begin{solution}
The answer is $321$.
\end{solution}

\begin{problem}
$BBWBWBBWBBB$ shows what happens if $8$ black marbles and $3$ white marbles are to be arranged in a row. Let $p$ be the probability that every white marble are always adjacent to black marbles to their left and right. If $p=\frac{m}{n}$ where $m$ and $n$ are relatively prime integers, compute $m+n$.
\end{problem}

\begin{solution}
The answer is $40$.
\end{solution}

\begin{problem}
If there are ten seats in a certain row at a movie theater, compute the number of ways that April, Bob, Cindy, and Dylan choose to sit in seats apart, assuming that there are none seated in this row when they arrive at the movie theater.
\end{problem}

\begin{solution}
The answer is $840$.
\end{solution}

\begin{problem}
In a triangle $ABC$, if $AB=221$, $BC=238$, $AC=255$, the angle bisector of $A$ intersects $\overline{BC}$ at point $M$, and the angle bisector of $B$ intersects $\overline{AC}$ at $N$. Let $P$ and $Q$ be perpendicular feet from $C$ to $\overline{AM}$ and $\overline{BN}$, respectively. If the ratio of $PQ$ to $AB$ can be written as $\frac{m}{n}$ for relatively prime positive integers, compute $m+n$.
\end{problem}

\begin{solution}
The answer is $21$.
\end{solution}

\begin{problem}
The distance between the point $(1,2,3)$ and the plane $z=x+2y+3$ can be written as $\frac{m}{\sqrt{n}}$ where $m$ and $n$ are square-free integers, given that the distance between a point $(a,b,c)$ off the plane $Ax+By+Cz+D=0$ is the length of the shortest distance from the point and the plane. Compute $m+n$.
\end{problem}

\begin{solution}
The answer is $11$.
\end{solution}

\begin{problem}
Given a square $ABCD$ whose side length is $3$, draw a diagonal $\overline{BD}$ and plot a point $E$ such that $BE:ED=2:1$. Then, there are four triangles $AEB$, $BEC$, $CED$, and $DEA$. Let $O_1$, $O_2$, $O_3$, $O_4$ be the circumcenter of respective triangles. The area of a quadrilateral $O_1O_2O_3O_4$ can be written as $\frac{m}{n}$ where $m$ and $n$ are relatively prime positive integers. Compute $m+n$.
\end{problem}

\begin{solution}
The answer is $11$.
\end{solution}

\begin{problem}
Given a square $ABCD$ whose side length is $2$, draw a diagonal $\overline{BD}$ such that a square has two adjacent right isosceles triangles $ABD$ and $CBD$. If there exists a point $P$ on a segment $\overline{AB}$ such that $\overline{DP}$ cuts the angle $\angle ADB$ such that $m\angle ADP : m \angle BDP = 1:2$, the ratio of $AP$ to $BP$ can be written as $\frac{\sqrt{m}-n}{p}$ where $m$, $n$, and $p$ are square-free positive integers. Compute $m+n+p$.
\end{problem}

\begin{solution}
The answer is $6$.
\end{solution}

\begin{problem}
Compute the number of non-congruent non-degenerate rectangles with integer side lengths whose area is at most $15$.
\end{problem}

\begin{solution}
The answer is $24$.
\end{solution}

\begin{problem}
How many $4$-digit positive integers include at least one digit of $3$, assuming that the thousand's digit can be $3$? In other words, count the number of $4$-digit integers such that at least one of the hundreds digit, tens digit or ones digit is $3$.
\end{problem}

\begin{solution}
The answer is $2439$.
\end{solution}

\begin{problem}
How many integers between $100$ and $999$, inclusive, contain at least one digit equal to $7$?
\end{problem}

\begin{solution}
The answer is $252$.
\end{solution}

\begin{problem}
Given a set of integers $\{1,2,3,4,\cdots,11\}$, compute the number of different integers that can be written as the sum of four different numbers in the given set.
\end{problem}

\begin{solution}
The answer is $29$.
\end{solution}

\begin{problem}
Given a set of $12$ points equally spaced around a round circle, if three distinct points are chosen out of the given points, compute the number of scalene triangles.
\end{problem}

\begin{solution}
The answer is $168$.
\end{solution}

\begin{problem}
There are $17$ green, $17$ blue, and $17$ yellow beads in a bag. Compute the number of beads that should be eliminated in total such that the ratio of green beads to yellow beads equals $5:6$ and the ratio of green beads to blue beads equals $2:3$.
\end{problem}

\begin{solution}
The answer is $14$.
\end{solution}

\begin{problem}
Compute the number of four-digit positive integers such that the product of the hundreds digit and tens digit does not exceed $4$.
\end{problem}

\begin{solution}
The answer is $2430$.
\end{solution}

\begin{problem}
Given a ten-digit keypad, the password must consist of five digits such that any pair of adjacent digits consists of two distinct numbers. If there are $n$ possible passwords, compute the number of positive divisors of $n$.
\end{problem}

\begin{solution}
The answer is $36$.
\end{solution}

\begin{problem}
If a triple of positive integers $(r,s,t)$ satisfies the following condition : $1\leq r, s, t \leq 3$, and the greatest common divisor of $r$, $s$, and $t$ is $1$, compute the number of distinct triples of $(r,s,t)$.
\end{problem}

\begin{solution}
The answer is $25$.
\end{solution}

\begin{problem}
In how many ways can 10 be partitioned into at most three whole numbers? Here, a whole number is a non-negative integer.
\end{problem}

\begin{solution}
The answer is $14$.
\end{solution}

\begin{problem}
A group of six students, riding in an elevator, noticed that there are three floors left to get off. If a different number of students must get off the elevator at each floor, with at least one student per floor, in how many ways can all students get off the elevator?
\end{problem}

\begin{solution}
The answer is $360$.
\end{solution}

\begin{problem}
If a group of five people must join four clubs, where there could be some club with no member, in how many ways can they join the clubs if there are only two groups with the same number of members? Here, two or more clubs with no member have the same number of members.
\end{problem}

\begin{solution}
The answer is $780$.
\end{solution}

\begin{problem}
Given a urn that contains 4 blue beads and 6 yellow beads, if four beads are selected at random, then the probability that at least three yellow beads are selected can be written as $\frac{m}{n}$ where $m$ and $n$ are relatively prime integers. Compute $m+n$.
\end{problem}

\begin{solution}
The answer is $61$. The probability is $19/42$.
\end{solution}

\begin{problem}
If three fair die are thrown at a time, let $a$, $b$, and $c$ be the face values that appear on top for each throw. Let $p$ be the probability that $ab=c$. If $p=\frac{m}{n}$ where $m$ and $n$ are relatively prime positive integers, compute $m+n$.
\end{problem}

\begin{solution}
The answer is $115$, where $m/n = 7/108$.
\end{solution}

\begin{problem}
Determine the largest integer value of $k$ such that $10^k$ divides $\binom{1000}{499}$, where $\binom{1000}{499}$ equals $\frac{1000!}{{499!}{501!}}$.
\end{problem}

\begin{solution}
The answer is $4$. First, we can calculate the $5$-adic number of $\binom{1000}{499}$ by
\begin{itemize}
\item $\lfloor \frac{1000}{5}\rfloor + \lfloor \frac{1000}{25} \rfloor + \lfloor \frac{1000}{125} \rfloor + \lfloor \frac{1000}{625} \rfloor = 249$.
\item $\lfloor \frac{499}{5}\rfloor + \lfloor \frac{499}{25} \rfloor + \lfloor \frac{499}{125} \rfloor = 121$.
\item $\lfloor \frac{501}{5}\rfloor + \lfloor \frac{501}{25} \rfloor + \lfloor \frac{501}{125} \rfloor = 124$.
\end{itemize}
such that $v_5(\frac{1000!}{499!501!})=249-121-124=4$. Thus, $10^4$ is the largest power of $10$ that divides $\binom{1000}{499}$.
\end{solution}

\begin{problem}
If $y=mx+17$ for $\frac{1}{7}<m<k$, there is no lattice point for $x=0, 1, 2, \cdots, 119$. The maximum value of $k$ can be written as $\frac{p}{q}$ where $p$ and $q$ are relatively prime positive integers. Determine $p+q$. 
\end{problem}

\begin{solution}
The answer is $135$. In order to tackle this problem, we must know how the lattice point works. First, draw the line with the slope of $\frac{1}{7}$ passing through $(0,17)$. Then, the graph of $y=\frac{1}{7}x+17$ passes through $(119,34)$. Notice that at $(118,34)$, the slope may change into $\frac{34-17}{118-0}=\frac{17}{118}$. Since the graph should not have lattice points as solution, it should not cross $(118,34)$. Perform the same analysis for $y=33$, $32$, $31$, and so on. We get that out of all possible slopes, $\frac{17}{118}$ must be the smallest value that covers all cases. Hence, $\frac{17}{118}$ must be the largest value of $k$. The answer must be $17+118=135$.
\end{solution}

\begin{problem}
How many positive integers less than or equal to $2023$ satisfy the following property such that the product of the digits equals $8$?
\end{problem}

\begin{solution}
The answer is $25$. Perform case-works on the number of digits such integer may have.
\begin{itemize}
    \item one-digit number : $8$.
    \item two-digit number : $81$, $42$, $24$, $18$.
    \item three-digit number : $811$, $181$, $118$, $421$, $412$, $241$, $214$, $142$, $124$, $222$.
    \item four-digit number : same as the third case by fixing the thousands digit as $1$.
\end{itemize}
Hence, there are $1+4+10+10=25$.
\end{solution}

\begin{problem}
Given a right triangle $ABC$, where $B$ is a right angle, if an angle bisector of $\angle BAC$ is drawn such that it intersects $\overline{BC}$ at $D$, assume that $AB=4$ and $BD=3$. The area of the triangle can be rounded down to an integer value of $N$. Determine the exact value of $N$.
\end{problem}

\begin{solution}
Let $CD=3k$ and $AC=4k$, by angle bisector theorem. Then, 
\begin{align*}
(4k)^2&=4^2+(3k+3)^2\\
16k^2&=16+9k^2+18k+9\\
0&=7k^2-18k-25\\
0&=(7k-25)(k+1)
\end{align*}
Hence, the area of the triangle can be written as 
\begin{align*}
\frac12\cdot4\cdot(3+3k)&=2(3+3k)\\
&=2(3+\frac{75}{7})\\
&=2(\frac{96}{7})\\
&=\frac{192}{7}
\end{align*}
If $\frac{192}{7}$ is rounded down, then $N=27$.
\end{solution}

\begin{problem}
Given a circle centered at $O$, there exists a chord $\overline{AD}$ located on one side of the circle. Assume that $B$ and $C$ are located on the minor arc formed by $AD=8$. If $ABCD$ is a cyclic quadrilateral with the largest possible area, and the central angle formed by the minor arc $AD$ has the measure of $135^\circ$, the area of $ABCD$ can be written as $a(\sqrt{b}-c)$ where $a$, $b$, and $c$ are positive integers, and $b$ is a square-free integer. Determine $a+b+c$.
\end{problem}

\begin{solution}
The answer is $35$. The largest cyclic quadrilateral, satisfying the given condition, is an isosceles trapezoid. Suppose otherwise, then you can always find the other point on the minor arc that gives larger area to reach contradiction. Since the central angle has the measure of $135^\circ$, the angle measure of $\angle DAB$ or $\angle ADC$ are $45^\circ$.\\
\bigskip
Let $AB=BC=CD=k\sqrt{2}$ for some $k$. Then, $k+k\sqrt{2}+k=k(2+\sqrt{2})=8$. Since the area of $ABCD$ can be written as 
\begin{align*}
\frac{1}{2}(8+k\sqrt{2})k&=4k+\frac{k^2\sqrt{2}}{2}\\
&=\frac{32}{2+\sqrt{2}}+\frac{64}{(2+\sqrt{2})^2}\cdot\frac{\sqrt{2}}{2}\\
&=\frac{32}{2+\sqrt{2}}+\frac{32\sqrt{2}}{6+4\sqrt{2}}\\
&=\frac{32}{2+\sqrt{2}}+\frac{16\sqrt{2}}{3+2\sqrt{2}}\\
&=\frac{32}{2+\sqrt{2}}+16\sqrt{2}(3-2\sqrt{2})\\
&=16(2-\sqrt{2})+48\sqrt{2}-64\\
&=32-16\sqrt{2}+48\sqrt{2}-64\\
&=32(\sqrt{2}-1)
\end{align*}
Hence, $a=32$, $b=2$, and $c=1$. Thus, the sum $a+b+c$ equals $35$.
\end{solution}

\begin{problem}
If the product $\sin(\frac{\pi}{5})\sin(\frac{2\pi}{5})\sin(\frac{3\pi}{5})\sin(\frac{4\pi}{5})$ can be written as $\frac{m}{n}$ where $m$ and $n$ are relatively prime positive integers, determine $m+n$.
\end{problem}

\begin{solution}
The answer is $21$. Let $\sin(5\theta)=0$ for $\theta=0$, $\frac{\pi}{5}$, $\frac{2\pi}{5}$, $\frac{3\pi}{5}$, and $\frac{4\pi}{5}$.
\begin{align*}
    \sin(5\theta) &= \binom{5}{1}\cos^4(\theta)\sin(\theta)-\binom{5}{3}\cos^2(\theta)\sin^3(\theta)+\binom{5}{5}\sin^5(\theta)\\
    &= 5(1-\sin^2(\theta))^2\sin(\theta)-10(1-\sin^2(\theta))\sin^3(\theta)+\sin^5(\theta)\\
    &= 5(1-2\sin^2(\theta)+\sin^4(\theta))\sin(\theta)-10(\sin^3(\theta)-\sin^5(\theta))+\sin^5(\theta)\\
    &=5\sin(\theta)-10\sin^3(\theta)+5\sin^5(\theta)-10\sin^3(\theta)+10\sin^5(\theta)+\sin^5(\theta)\\
    &=\sin(\theta)(16\sin^4(\theta)-20\sin^3(\theta)+5)
\end{align*}
Hence, by Viete's formula, $\sin(\frac{\pi}{5})\sin(\frac{2\pi}{5})\sin(\frac{3\pi}{5})\sin(\frac{4\pi}{5})=\frac{5}{16}$. Thus, $m+n=5+16=21$.
\end{solution}

\begin{problem}
A pyramid has a square base with sides of length $1$ and has lateral faces that are equilateral triangles. A cube is placed within the pyramid so that one face is on the base of the pyramid and its opposite face has all its vertices only on the lateral faces of the pyramid. The volume of the cube can be written as $\frac{\sqrt{a}}{b}$ where $a$ and $b$ are positive integers. Determine $a+b$.
\end{problem}

\begin{solution}
Let $k$ be the length of the edge of the inscribed cube. Then, by using similarity ratio of heights and bases, we get 
\begin{align*}
\frac{\frac12-\frac{k}{\sqrt{2}}}{\frac12}&=\frac{k}{\frac{\sqrt{2}}{2}}\\
\frac{k}{2}&=\frac{\sqrt{2}}{4}-\frac{k}{2}\\
k&=\frac{\sqrt{2}}{4}
\end{align*}
Hence, the volume must be $(\frac{\sqrt{2}}{4})^3=\frac{2\sqrt{2}}{64}=\frac{\sqrt{2}}{32}$. Thus, the answer is $34$.
\end{solution}

\begin{problem}
Given a regular icosahedron, if each vertex is cut by a plane such that it leaves a smaller regular pentagon as its cross-section, we may call it a truncated icosahedron. Here, we assume that the size of the regular pentagon formed by a cross-section does not intersect with any other pentagon in the solid. Let $N$ be the number diagonals of the solid passing through the interior of the solid. Determine the remainder when $N$ is divided out by $1000$.
\end{problem}

\begin{solution}
According to Euler's formula, we get the number of edges as $90$, the number of faces as $32$, and the number of vertices as $60$. We solve this problem using complementary counting method.\\
\bigskip
First, the total number of ways to connect two different vertices of the truncated icosahedron equals $\binom{60}{2}=1770$. Second, the total number of edges and diagonals on the faces are $90+(20\times9+12\times5)=330$. Hence, the difference between the two numbers equals $1440$. Thus, the remainder when $1440$ is divided by $1000$ equals $440$. The answer is $440$.
\end{solution}

\begin{problem}
Bob went to a store that sells two types of packs of candies - one with 20 candies and the other with 23 candies. Determine the sum of the second and third largest number of candies he cannot buy.
\end{problem}

\begin{solution}
Apply McNugget's Theorem to get $20\cdot23-20-23=417$. Since $417$ is the largest number of candies he cannot buy, $417-20$ or $417-23$ cannot be reached either. Hence, $397+394=791$. The answer is $791$.
\end{solution}

\begin{problem}
If $\frac{2023!}{20!23!}$ is written in base $7$, determine the terminal zeros. Here, if the number is written as $\overline{1234000}_7$, there are three terminal zeros in base $7$.
\end{problem}

\begin{solution}
The answer is $330$. Since we are looking for the $7$-adic number of $\frac{2023!}{20!23!}$, we calculate the following numbers.
\begin{itemize}
\item $\lfloor \frac{2023}{7}\rfloor + \lfloor \frac{2023}{49} \rfloor + \lfloor \frac{2023}{343}\rfloor = 335$.
\item $\lfloor \frac{20}{7} \rfloor = 2$.
\item $\lfloor \frac{23}{7} \rfloor =3$.
\end{itemize}
Hence, $v_7(\frac{2023!}{20!23!})=335-2-3=330$. Hence, there are $330$ terminal zeros in base-$7$ expression.
\end{solution}

\begin{problem}
Given a triangle $ABC$ with $AB=15$, $AC=41$, and $BC=52$, there exists a circle centered at $O$, tangent to $\overline{BC}$, $\overrightarrow{AB}$ and $\overrightarrow{AC}$. The length $AO$ can be written as $a\sqrt{b}$ where $b$ is a square-free integer. Determine $a+b$.
\end{problem}

\begin{solution}
The area of the triangle equals $234$, retrieved by using Heron's formula. First, $s=\frac{15+41+52}{2}=54$. Then, area equals $\sqrt{54\cdot 39 \cdot 13 \cdot 2}=234$. Hence, the inradius of the triangle equals $\frac{18}{3}$. Let $D$, $E$ and $F$ be the points of tangency to $\overline{AB}$, $\overline{AC}$ and $\overline{BC}$. Then, length chasing results in $AD=2$.\\
\bigskip
Since $O$ is the excenter of $A$, we will use similarity ratio to solve for $AO$. The excircle from $O$ to rays $AB$ and $AC$ result in points of tangency, i.e., $G$ and $H$, respectively. Then, $AG=AH$, by definition of angle bisector. Let $BG=\alpha$ and $CH=\beta$. Then, $\alpha+\beta=52$ and $15+\alpha=41+\beta$. Solving the system of equation results in $\alpha=39$ and $\beta=13$. Hence, $AD:AG=AI:AO$ if $I$ is the incenter. Thus, $2:54=\frac{\sqrt{205}}{3}:AO$. This indicates that $AO=9\sqrt{205}$. Therefore, the answer is $214$. 
\end{solution}

\begin{problem}
If $p(x)=x^3-15x^2+11x-97$ has roots $r$, $s$, and $t$, then $\lvert \frac{1}{(r-1)^2}+\frac{1}{(s-1)^2}+\frac{1}{(t-1)^2} \rvert$ can be written as $\frac{m}{n}$ where $m$ and $n$ are relatively prime positive integers. Determine $m+n$.
\end{problem}

\begin{solution}
The answer is $759$. By Viete's formula, $p(x)=(x-r)(x-s)(x-t)$. In order for $r-1$, $s-1$, and $t-1$ to be solutions, we must find $p(x+1)=0$, where $p(x+1)=x^3-12x^2-16x-100$. Since we must find the roots that are reciprocals, we turn the coefficients backward so that $q(x)=-100x^3-16x^2-12x+1$ have roots $\frac{1}{r-1}$, $\frac{1}{s-1}$, and $\frac{1}{t-1}$.\\
\bigskip
Let $\frac{1}{r-1}=r'$, $\frac{1}{s-1}=s'$, and $\frac{1}{t-1}=t'$. We apply Newton's identity so that $S_1=r'+s'+t'$ and $S_2=(r')^2+(s')^2+(t')^2$, where
\begin{align*}
-100S_2-16S_1-12(2)&=0\\
100S_2&=-16S_1-24\\
S_2&=-\frac{134}{625}
\end{align*}
Hence, $|S_2|=\frac{134}{625}$, so $59+625=759$.
\end{solution}

\begin{problem}
A parallelogram $ABCD$ satisfies the following property. First, $\overline{AB}$ is parallel to $\overline{CD}$. Second, $\angle B$ and $\angle D$ are acute angles. Third, $AD>AB$. There exists a point $E$ on $\overline{AD}$ such that a ray from $B$ is drawn to $\overline{AD}$ such that its point of intersection is labeled as $E$, and the ray can be reflected about the side $\overline{AD}$ to $C$ such that $\angle ECD$ is a right angle. If $m\angle ABE : m \angle CBE = 1:2$ and $BE=12$, then the length $AD$ can be written as $a+\sqrt{b}$ where $a$ and $b$ are positive integers. Determine $a+b$.
\end{problem}

\begin{solution}
The answer is $186$. Let $\theta=m\angle ABE$. Since $\triangle ECD$ is a right triangle, we compute that $2\theta+3\theta=90^\circ$. Hence, $\theta=18^\circ$. Let $F$ be the perpendicular foot from $E$ to $\overline{BD}$. Then, the triangle $EBF$ forms a right triangle with angle measures $36^\circ$, $54^\circ$ and $90^\circ$. Using basic trigonometric rules, we get
\begin{align*}
    \cos(2\theta)&=\frac{BF}{BE}\\
    &=\frac{BF}{12}\\
    \frac{\sqrt{5}+1}{4}&=\frac{BF}{12}\\
    BF&=3\sqrt{5}+3\\
    BC&=6\sqrt{5}+6
\end{align*}
Since $AD=BC=\sqrt{180}+6$, we get the answer $180+6=186$.
\end{solution}

\begin{problem}
A triangle $ABC$ has $\angle B$ as a right angle and $AC=25$. There exists a point $D$ on $\overline{AB}$ such that $AD:BD=1:2$ and another point $E$ on $\overline{BC}$ such that $BE=AD$. If $\overline{AE}$ and $\overline{CD}$ intersect at $F$ such that $m\angle CFE = 45^\circ$, find the area of $\triangle ABC$.
\end{problem}

\begin{solution}
The answer is $150$. Let $m\angle BAE=\theta$. Then, $m\angle BDC = \theta + 45^\circ$. Label $AD=k$, $BD=2k$ and $BE=k$. Then, $\tan(\theta)=\frac{1}{3}$. Apply the law of tangents such that
\begin{align*}
\tan(\theta+45^\circ)&=\frac{\tan(\theta)+\tan(45^\circ)}{1-\tan(\theta)\tan(45^\circ)}\\
&=\frac{\frac13+1}{1-\frac13}\\
&=2
\end{align*}
Hence, $BC=4k$. Since $AB=3k$ and $BC=4k$, we know that $AC=5k$. Hence, $AC=25=5k$ implies that $k=5$.\\
\bigskip
The area of the triangle $ABC$ can be written as $\frac12\times3k\times4k=6k^2=6(25)=150$.
\end{solution}

\begin{problem}
How many ordered triples $(a,b,c,d)$ all chosen out of the first 10 positive integers satisfy $a<b<c<d$ where $a$, $c$ are odd, and $b$, $d$ are even?
\end{problem}

\begin{solution}
The answer is $35$.
\end{solution}

\begin{problem}
Let $N$ be the largest integer $n$ such that $\log_{1000}(n)$ is less than $1$. Determine the number of positive divisors of $N$.
\end{problem}

\begin{solution}
The answer is $8$. Notice that the largest possible value of $n$ is $999$ since $\log_{1000}(999) < 1$. Hence, the number of positive factors of $999$ can be easily be found by $(3+1)(1+1)=8$ because $999=3^3\times37$.
\end{solution}

\begin{problem}
A square with lengths of $4$ is cut into four congruent isosceles triangles. Let $G_1$, $G_2$, $G_3$, and $G_4$ be the centroids of each triangle, respectively. The area of circumcircle of $G_1G_2G_3G_4$ can be written as $\frac{m\pi}{n}$ for relatively prime positive integers $m$ and $n$. Find $m+n$.
\end{problem}

\begin{solution}
Let $O$ be the center of $G_1G_2G_3G_4$. The distance from $O$ to $G_1$, without loss of generality, is $\frac{4}{3}$. Therefore, the area of circumcircle is $\frac{16\pi}{9}$. Thus, the answer is $25$.
\end{solution}

\begin{problem}
Given a right triangle $ABC$ where $B$ is a right angle, there exists $D$ on $\overline{AC}$ such that $BD$ is the height. If $AD=3$ and $CD=5$, find the integer closest to the perimeter of $ABC$.
\end{problem}

\begin{solution}
First, notice that $BD=\sqrt{15}$. Apply Pythagorean Theorem twice to get $AB=\sqrt{24}$ and $BC=\sqrt{40}$. Hence, the perimeter is $\sqrt{24}+\sqrt{40}+15$. The closest integer is $26$. Hence, the answer is $26$.
\end{solution}

\begin{problem}
In a singles fencing tournament with $1000$ players who can lose $5$ matches before elimination, determine the difference between the maximum and minimum number of matches a champion plays.
\end{problem}

\begin{solution}
At most, he or she can lose $4$ matches. At least, he or she can lose $0$ matches. The difference between these number of matches is $4$.
\end{solution}

\begin{problem}
Bob lists all possible subsets of $\{1,2,3,4,5,6\}$, including improper ones. He multiplies number(s) in each subset, and add them up. What is this number?
\end{problem}

\begin{solution}
Consider $f(x)=(x-1)(x-2)(x-3)(x-4)(x-5)(x-6)$. Then, $f(-1)=7!=1+1+2+3+4+5+6+1\cdot2+1\cdot3+\cdots+5\cdot6+\cdots+1\cdot2\cdot3\cdot4\cdot5\cdot6$. Hence, $7!-1$ is what we want. The answer is $5039$.
\end{solution}

\begin{problem}
Consider a polynomial $p(x)=x^3-x^2+2x-1$ whose roots are $r$, $s$, and $t$. If $\frac{r^3}{s^2+t^2}+\frac{s^3}{r^2+t^2}+\frac{t^3}{r^2+s^2}$ can be written as $\frac{m}{n}$ where $m$ and $n$ are relatively prime positive integers, determine $m+n$.
\end{problem}

\begin{solution}
First, Viete's formula states that $r+s+t=1$, $rs+st+tr=2$ and $rst=1$. This implies that $\frac{r^3}{s^2+t^2}+\frac{s^3}{r^2+t^2}+\frac{t^3}{r^2+s^2}=\frac{r^3}{-3-r^2}+\frac{s^3}{-3-s^2}+\frac{t^3}{-3-t^2}=\frac{17}{7}$. Hence, $m+n=17+7=24$. The answer is $24$.
\end{solution}

\begin{problem}
Let $ABCD$ be a parallelogram with $\angle A$, $\angle C$ be an acute angle. There exists some $P$ at the angle bisector of $\angle A$ such that $P$ is equidistant from $BC$, $AD$, and $AB$. Let $Q$ be the perpendicular foot from $D$ to $\overline{BC}$. If $\angle BDQ$ is congruent to $\angle BAD$, and $BD=10$, determine the length $AB$.
\end{problem}

\begin{solution}
The answer is IDK
\end{solution}

\begin{problem}
Given an obtuse triangle $AB$, $BC$ and $AD$, if $AB=12$, $BC=5$, and $AC^2$ is the largest prime number smaller than $230$, let $P$ be a point on $AC$ such that the measure of $\angle ABP$ is three times the measure of $\angle CBP$. Determine $\frac{AP}{CP}$.
\end{problem}

\begin{solution}
I have no idea.
\end{solution}

\begin{problem}
For variables $a$, $b$, and $c$, if $a+b+c=1$, find the value of $a^2b^2c^2$ if $\frac{1}{a+b}+\frac{1}{b+c}+\frac{1}{a+c}=1$.
\end{problem}

\begin{solution}
Do algebraic manipulation using $a+b+c=1$ to conclude that $abc=-1$. Hence, $a^2b^2c^2=1$. The answer is $1$.
\end{solution}

\begin{problem}
The sum of real solutions to a quartic equation $x^4-2x^3+\frac12x^2-2x+1=0$ can be written as $\frac{a+\sqrt{b}}{a}$ where $a$ and $b$ are positive integers such that $b$ is a square-free integer. Find the sum of $a$ and $b$.
\end{problem}

\begin{solution}
Divide all sides by $x^2$. Then, notice that $(x+1/x)^2=1\pm \frac{\sqrt{10}}{2}$. Hence, $x+\frac1x=1+\frac{\sqrt{10}}{2}$, so the sum of real solutions equals $\frac{2+\sqrt{10}}{2}$. The answer is $12$.
\end{solution}